---
title: "Mispriced Diamonds"
author: "Poro Burman"
date: "7/8/2020"
output:
  pdf_document: default
  html_document: default
---

**load the 'mispriced_diamonds_data.txt' file**  
```{r}
mispriced_diamonds <- read.csv("Mispriced_Diamonds_data.txt")
```  

**load 'ggplot2 package' to visualize the data**  
```{r}
library("ggplot2")
```  

**create a scatter plot between the 3 different variables of the dataset**  
```{r}
ggplot(data = mispriced_diamonds, aes(x=carat, y=price, colour=clarity)) + 
        geom_point()
```  

**the image looks to cluttered so going to reduce alpha to 0.3 to get a better view**  
```{r}
ggplot(data = mispriced_diamonds, aes(x=carat, y=price, colour=clarity)) + 
        geom_point(alpha=0.3)
```  

**looking at the image now, it seems that there are a lot of outliers beyond 2.5**  
**carat. These values aren't required so now I'll plot the data without those**  
**points**  
```{r}
ggplot(data = mispriced_diamonds[mispriced_diamonds$carat < 2.5,], aes(x=carat,
       y=price, colour=clarity)) + geom_point(alpha=0.3)
```  

**I'm going to add the 'geom_smooth' to this graph so that I can get a view of the**  
**lines representing averages for each of the clarities.**  
```{r}
ggplot(data = mispriced_diamonds[mispriced_diamonds$carat < 2.5,], aes(x=carat,
       y=price, colour=clarity)) + geom_point(alpha=0.3) + geom_smooth()
```  

**Now when one looks at the figure, one will realize that there seems to be some**   
**intersections between the clarities. The pricing of different clarities shouldn't**  
**intersect. Looking at carat = 0.7, there seems to be diamonds of different clarities**  
**which might be priced together. This is also observed at carat = 1.7 and carat = 2.1.**  
**This shows that there might be a possibility that the prices of the diamonds**  
**might be incorrectly labelled for these carats.**